IML Term project

### 2022-12-03 main_markdown.rmd
paper updates

Columns selected by correlation

```{r preprocess data}
# Create class2
npfOrig$class2[npfOrig$class4 == "nonevent"] <- 0
npfOrig$class2[npfOrig$class4 != "nonevent"] <- 1

@@

# Select global and 16.8 m high values
npf <- data.frame(npfOrig[, (5:6)], npfOrig[, (13:16)], npfOrig[, (27:30)], 
                  npfOrig[, (41:42)], npfOrig[, (53:54)], npfOrig[, (63:72)],
                  npfOrig[, (83:88)], npfOrig[, (99:104)])

# Poistetaan sarakkeet id, date, class4, partlybad
npfOrig <- npfOrig[, -(1:4)]
# Calculate the correlation matrix
cm <- cor(npf)

# Order variables by 1st principal component
corrplot(cm, order = "FPC", tl.cex = 0.5, tl.col = "black")

# Puolitetaan training data jotta saadaan realistinen testausdata
set.seed(42)
idx <- sample(nrow(npfOrig), nrow(npfOrig)/2)
npf_train <- npfOrig[idx, ]
npf_test <- npfOrig[-idx, ]
```

>>>>

### Creating training and testing data
```{r preprocess data, echo=FALSE}
# Create class2
npfOrig$class2[npfOrig$class4 == "nonevent"] <- 0
npfOrig$class2[npfOrig$class4 != "nonevent"] <- 1

@@

# Remove columns id, date, class4, partlybad
npfData <- npfOrig[, -(1:4)]

# Sample half of the data for training and testing sets
set.seed(42)
idx <- sample(nrow(npfData), nrow(npfData)/2)
npf_train <- npfData[idx, ]
npf_test <- npfData[-idx, ]
```

### Selecting columns by correlation
```{r correlation plot, echo=FALSE}
# Original correlation s
cmData <- cor(npfData)
corrplot(cmData, order = "FPC", tl.cex = 0.5, tl.col = "black")

# Select global and 16.8 m high values for correlation plot
npf168 <- data.frame(npfOrig[, (5:6)], npfOrig[, (13:16)], npfOrig[, (27:30)], 
                  npfOrig[, (41:42)], npfOrig[, (53:54)], npfOrig[, (63:72)],
                  npfOrig[, (83:88)], npfOrig[, (99:104)])
cm168 <- cor(npf168)
corrplot(cm168, order = "FPC", tl.cex = 0.5, tl.col = "black")
```
